Segregation in Vienna's primary schools?

### 2021-01-09 _post/2020-03-02-primary-schools-in-vienna/primary-schools-in-vienna.Rmd
removed old, invalid token

```{r include=FALSE}
df_main <- readr::read_rds(here("_blog_data", "Vienna_primary_schools", "df_main.rds"))
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1Ijoiem9vd2FsayIsImEiOiJjazFjMW52NWIwZDVjM21scmE1Y296MnUxIn0.ZXSu71B2VjyBwlUldNUtLg")
```

>>>>

```{r include=FALSE}
df_main <- readr::read_rds(here("_blog_data", "Vienna_primary_schools", "df_main.rds"))
